Parsing Tweets into Universal Dependencies

### 2017-12-15 paper.tex
fix tab 7

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it Tokenization System & $F_1$ \\
		\hline
		Stanford CoreNLP & 92.1 \\
		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.6 \\
		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rrcc}
		\hline
		\it Pipeline stage & Score & Ours & SOTA \\
		\hline
		Tokenization  & \it $F_1$ & 98.3 & 96.6 \\		
		POS tagging &  \it  $F_1$ & 93.7 & 92.1 \\
		UD parsing & \it LAS $F_1$ & 74.1 & 70.3 \\
		\hline
	\end{tabular}
	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} \yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent} }
\end{table}

>>>>

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it Tokenization System & $F_1$ \\
		\hline
		Stanford CoreNLP & 92.1 \\
		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.7 \\
		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rrcc}
		\hline
		\it Pipeline stage & Score & Ours & SOTA \\
		\hline
		Tokenization  & \it $F_1$ & 98.3 & 96.6 \\		
		POS tagging &  \it  $F_1$ & 93.7 & 92.1 \\
		UD parsing & \it LAS $F_1$ & 74.1 & 70.3 \\
		\hline
	\end{tabular}
	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} %\yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent}
	}
\end{table}
